European or American? A re-examination of the transatlantic influence over the IMF

### 2025-09-02 manuscript/manuscript.qmd
Appendix: 2nd para

>>>>

@tbl-results-fiscal reveals patterns that largely reinforce our main findings while adding important nuance. Consistent with our baseline results, US influence is significantly associated with fewer overall IMF conditions. This pattern extends to fiscal conditions, where US influence is associated with a substantial reduction, though this effect is only marginally significant ($p < 0.1$), likely due to the much smaller sample size ($N=31$ vs. $N=93$ for total conditions). Interestingly, European influence shows the opposite pattern: it is associated with a significant increase in fiscal conditions ($p < 0.05$), suggesting that European powers may advocate for more extensive fiscal reforms when they have influence over IMF lending decisions. This finding supports arguments in the current literature that Europe, if anything, has more fully internalized neoliberal economic orthodoxy and the principles of the "Washington Consensus" than the United States, and may view austerity-oriented policies as intrinsically beneficial [@lutz2014; @dyson2010].
